---
name: Linda Cabrera-Orellana
position: "Data Scientist"
address: |
         | San Miguel 11, 18194 Granada, España
profilepic: linda.jpeg
phone: +34 624 609 588 
www: lindajzmin-website.netlify.app
email: "lindaj.cabrera@gmail.com"
twitter: lindajzmin
github: lindajzmin
linkedin: lindajzmin
headcolor: 009ACD
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: false
always_allow_html: yes
header-includes: |
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(ggplot2)
library(dplyr)
library(ggrepel)
library(emojifont)
library(fontawesome)
library(kableExtra)
library(huxtable)
library(gridExtra)
library(sf)
library(rnaturalearth)
library(sfnetworks)
```


\paragraphstyle{I am a data scientist with a passion for data communication and data visualization. I have a background in mathematics and quantitative techniques for business management. I am currently working as online software instructor at Sociedad Ecuatoriana de Estadística.}


\section{\faGears Skills}

\subsection{Technical}

```{r techtable, results='markup'}
tribble(
   ~`Data Processing`, ~`Data Visualization`, ~Marketing, ~Others,
  "R -- Python -- MS Excel -- SPSS",
  "Power BI -- Shiny",
  "Google Analytics-- Canva",
  "SQL -- Git -- GitHub -- LaTeX"
) |>
  kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
  kable_styling(full_width = F, font_size = 9, latex_options = "HOLD_position") |> 
  row_spec(0, bold = T, color = "#009acd") |> 
  row_spec(1, bold = F, color = "#7f7f7f") |> 
  column_spec(column = 1:4, width = '4cm')
```

\subsection{Soft}

* Problem solving, Teamwork and Critical Thinking
* Initiative and Adaptability
* Compromise and Responsibility


\section{\faCode Projects}

```{r dev}
tribble(
  ~ name, ~ sum, ~ acronym, ~ type, ~ lang, ~ link,
  "Twitter data mining, text analysis, sentiment analysis and LDA.", 
  "Text Mining: Twitter data mining, text analysis, sentiment analysis and LDA.",
  "\\href{https://github.com/lindajzmin/text_mining}{\\tiny{\\faLink}}", 
  "Text Mining",
  "R",
  "\\href{https://github.com/lindajzmin/text_mining}{\\faGithub}",
  
  "Prospecting of cardholder consumption based on the line of business.", 
  "Data Science: Prospecting of cardholder consumption based on the line of business.", 
  "\\href{https://github.com/lindajzmin/project_datascience}{\\tiny{\\faLink}}", 
  "Clustering",
  "R",
  "\\href{https://github.com/lindajzmin/project_datascience}{\\faGithub}",

  "My web-site: Linda Cabrera", 
  "Linda Cabrera: Website contains my portfolio, posts and projects about data science and education.", 
  "Blog \\href{https://github.com/lindajzmin/mi_sitioweb}{\\tiny{\\faLink}}", 
  "Web-Site",
  "Html - CSS - R",
  "\\href{https://github.com/lindajzmin/mi_sitioweb}{\\faGlobe}"
) |> 
  brief_entries(with = lang, what = sum, when = link, .protect=FALSE)  
```



\section{\faBriefcase Professional Experience}

```{r experience}
tribble(
  ~ organization, ~ puesto, ~ loc, ~ dates, ~ details,
  "Sociedad Ecuatoriana de Estadística", "Software Instructor (remote)"," ", "04, 2022 - present", "Instructor of the \\textit{Software Management} module of the International Program for Statistics Applied to Scientific Research.",
  "Sociedad Ecuatoriana de Estadística", "Software Instructor (remote)"," ", "04, 2022 - present", "Instructor of the course Data Manipulation with R.",
  "R-Ladies Guayaquil", "Co-organizer (remote)", " ", "04, 2021 - present", "Organization of workshops and virtual events for the teaching of R and its applications.", 
    "R-Ladies Guayaquil", "Co-organizer (remote)", " ", "04, 2021 - present", "Collaboration in the organization of regional and international conferences of the R community.", 
  "Universidad Técnica de Machala", "Full-time Teacher (hybrid)","Machala, EC", "04, 2019 - 09, 2022", "Chair of Calculus, Statistics and Differential Equations.",
  "Universidad Técnica de Machala", "Full-time Teacher (hybrid)","Machala, EC", "04, 2019 - 09, 2022", "Member of the Quality Management and Accreditation Committee. Management of indicators.",
  "Universidad Técnica de Machala", "Full-time Teacher (hybrid)","Machala, EC", "04, 2019 - 09, 2022", "Creator of the fan page of the Food Engineering Career and Community Manager. URL:  \\textit{ https://www.facebook.com/alimentosutmach} ",
  "Corporación Eléctrica del Ecuador CELEC EP", "Programming and Quality Management Assistant", "Machala, EC", "04, 2013 - 02, 2017", "Implementation and Responsible for the Quality Management System ISO 9001-2015.",
  "Corporación Eléctrica del Ecuador CELEC EP", "Programming and Quality Management Assistant", "Machala, EC", "04, 2013 - 02, 2017", "Design and development of reports, dashboards or other tools for monitoring strategic information in MS Excel.",
  "Corporación Eléctrica del Ecuador CELEC EP", "Programming and Quality Management Assistant", "Machala, EC", "04, 2013 - 02, 2017", "Process management, control and monitoring of company indicators.",
  "Corporación Eléctrica del Ecuador CELEC EP", "Programming and Quality Management Assistant", "Machala, EC", "04, 2013 - 02, 2017", "Optimization of the inventory process. 30\\% annual reduction in inventory cost."
) |> 
  detailed_entries(organization, dates, puesto, loc, details, .protect=FALSE)
```


\section{\faUniversity Education}

```{r education}
tribble(
  ~ study, ~ university, ~ loc, ~ dates, ~ details,
    "Máster en Investigación Matemática", "Universitat Politècnica de València \\& Universitat de València","Valencia, SP", "2017 - 2018", "Methodological tools in mathematical research, Introduction to mathematical research, Mathematical modeling in industry, Applied Mathematics.",
    "Máster en Investigación Matemática", "Universitat Politècnica de València \\& Universitat de València","Valencia, SP", "2017 - 2018", "TFM: Algoritmos matemáticos para el tratamiento de señales financieras. URL: \\textit{http://hdl.handle.net/10251/111119}",
    "Ingeniera en Auditoría", "Escuela Superior Politécnica del Litoral", "Guayaquil, EC", "2009 - 2014", "Quantitative Methods 1-3, Financial Mathematics, Inferential Statistics, Sampling and Survey Design, Financial Administration, Database for Auditors, Sampling and Multivariate Analysis, Quality Engineering, Operational Auditing, Auditing of Computer Applications, among 34 subjects.",
  "Ingeniera en Auditoría", "Escuela Superior Politécnica del Litoral", "Guayaquil, EC", "2009 - 2014", "Tesis: Diseño de un sistema de gestión por procesos, aplicado a una empresa dedicada a la rectificación de motores. URL: \\textit{http://www.dspace.espol.edu.ec/xmlui/handle/123456789/39500}"
) |> 
  detailed_entries(study, dates, university, loc, details, .protect=FALSE)
```



\subsection{\faLightbulbO Courses}

```{r presentations}
tribble(
  ~ title, ~ link, ~ event, ~ date,
  "Women in Data Science Ecuador", "Universidad de Stanford - Sociedad Ecuatoriana de Estadística", " ", "04, 2022",
  "Bioestadística aplicada a la investigación científica", "Sociedad Ecuatoriana de Estadística", " ", "02, 2022",
  "useR! 2021 The R Conference", "The R Foundation for Statistical Computing c/o Institute for Statistics and Mathematics", " ", "07, 2021",
  "X Seminario Internacional de Estadística Aplicada", "Sociedad Ecuatoriana de Estadística", " ", "05, 2021",
  "Análisis de redes sociales usando Procesamiento de Lenguaje Natural", "Sociedad Ecuatoriana de Estadística", " ", "01, 2021",
  "Visualización y Analítica de Datos con Power BI", "SolOpt S.A.", " ", "07, 2020",
  "Getting and Cleaning Data","EdX", " ", "05, 2020",
  "R Programming","EdX", " ", "04, 2020"
) |> 
  detailed_entries(with = title, what = link, where = event, when = date, .protect=FALSE)  
```



\section{\faCertificate Certifications}

```{r dist}
tribble(
  ~ area, ~ org, ~ date,
    "Software Carpentry Instructor", "The Carpentries", "2021",
  "Data Scientist - Sociedad Ecuatoriana de Estadística", "SEE", "2021"
) |> 
  brief_entries(what = area, when = date, with = org, .protect = F)
```


\section{\faUser Memberships}

```{r org}
tribble(
  ~ org, ~ date,
  "R-Ladies Global \\href{https://twitter.com/RLadiesGye}{\\tiny{\\faLink}}", "since 2021",
  "Women in Data Science \\href{https://www.widsconference.org/ambassadors-2022.html}{\\tiny{\\faLink}}", "since 2022",
  "Organizing Committee, Latin R 2021, Latin American Conference for the use of R", "2021"
) |> 
  brief_entries(what = org, when = date, .protect = F)
```


\section{\faLanguage Languages}

* English:
    - Reading/Listening: Intermediate
    - Speech: Intermediate

* Spanish: Native



